### 2015-01-14 fundamentals/examples.tex
fixed weird sentence about cyclus having fuel cycle capabilities.. duh. it's an fcs...

The functionality and feasibility of the \Cyclus simulator is illustrated by demonstrations
of its fundamental simulation capabilities and growth via its
 community-driven \Cyclus development model.
The success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can 
advance in a community-driven development paradigm. Additionally, simple 
simulations as well as more complex recycling simulations demonstrate that 
\Cyclus possesses fuel cycle simulation capabilities.

@@

The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository
\item the archetypes created by researchers
\item isotopic composition data
\item historical facility deployment data
\item the \Cyclus \gls{GUI} tool Cyclist
\item fundamental analysis tools in the \Cyclus toolkit
\item tools for \Cyclus optimization, parallelization, and development
\end{itemize}
Taken together, these form an ecosystem of capabilites. Over time, this 
ecosystem will grow as archetype developers, kernel developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions.

@@

Results of some simple recycle scenarios run in \Cyclus follow. Beginning with a single
reactor simulation, open (no recycle), modified open, and closed (infinite-pass recycle) 
fuel cycles are compared to illustrate the resolution possible with \Cyclus.  The simulation
is then expanded to include multiple reactors in the same set of fuel cycles to demonstrate
the system-scale convergance to continuous material flow models.

@@

\begin{lstlisting}[language=diff]
  --- mod-open-1.xml	2014-10-08 08:31:33.892523173 -0500
  +++ closed-1.xml	2014-10-08 08:31:33.892523173 -0500
  @@ -108,7 +108,7 @@
           <fuel>         
             <incommodity>mox_fuel</incommodity>
             <inrecipe>lwr_mox_fuel</inrecipe>
  -          <outcommodity>spent_mox</outcommodity>
  +          <outcommodity>spent_fuel</outcommodity>
             <outrecipe>mox_spent_fuel</outrecipe>
           </fuel>
\end{lstlisting}
This results in the material flows in Figure \ref{fig:flowclosed}. Note
that the \Class{BatchReactor} always transmutes fuel into the same
composition, so the nuclide level flows are unrealistic for the full, 
multi-pass
recycle case.

@@

Figure \ref{fig:puseries1} shows the full-system plutonium buildup for open
(no recycle), modified open, and closed (infinite-pass recycle) \TODO{whats
the diff btw closed and the multi-pass from above? It's referred to as fully
closed multi-pass recycle, which is a bit confusing.} variations of
the scenario described above (all just a single reactor).  The figure was
generated directly from \Cyclus output data. After several batch cycles (near
month 300) in the modified open and closed cases, enough separated fissile
material accumulates in the fuel fabrication facility to generate a full
recycled batch.  When this batch is transmuted, more plutonium is burned than
created.  This results in a drop in the total fuel cycle system plutonium
inventory.  This pattern repeats roughly every 10 cycles (200 months) for the
modified open case and every 9 cycles (180 months) for the closed case.
Because the modified open scenario does not re-recycle material, it takes the
fabrication facility 1 cycle longer to accumulate a full batch of
fissile material.

>>>>

The functionality and feasibility of the \Cyclus simulator is illustrated by demonstrations
of its fundamental simulation capabilities and growth via its
 community-driven \Cyclus development model.
The success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can 
advance in a community-driven development paradigm. Additionally, simulation 
results for both once-through and more complex recycling scenarios demonstrate that 
\Cyclus possesses the fundamental fuel cycle simulation capabilities to 
contribute to the field.

@@

The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository
\item the archetypes created by researchers
\item isotopic composition data
\item historical facility deployment data
\item the \Cyclus \gls{GUI} tool Cyclist
\item fundamental analysis tools in the \Cyclus toolkit
\item tools for \Cyclus optimization, parallelization, and development
\end{itemize}
Taken together, these form an ecosystem of capabilities. Over time, this 
ecosystem will grow as archetype developers, kernel developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions.

@@

Results of some simple recycle scenarios run in \Cyclus follow. Beginning with a single
reactor simulation, open (no recycle), modified open, and closed (infinite-pass recycle) 
fuel cycles are compared to illustrate the resolution possible with \Cyclus.  The simulation
is then expanded to include multiple reactors in the same set of fuel cycles to demonstrate
the system-scale convergence to continuous material flow models.

@@

\begin{lstlisting}[language=diff]
  --- mod-open-1.xml	2014-10-08 08:31:33.892523173 -0500
  +++ closed-1.xml	2014-10-08 08:31:33.892523173 -0500
  @@ -108,7 +108,7 @@
           <fuel>         
             <incommodity>mox_fuel</incommodity>
             <inrecipe>lwr_mox_fuel</inrecipe>
  -          <outcommodity>spent_mox</outcommodity>
  +          <outcommodity>spent_fuel</outcommodity>
             <outrecipe>mox_spent_fuel</outrecipe>
           </fuel>
\end{lstlisting}

This results in the material flows in Figure \ref{fig:flowclosed}. Note
that the \Class{BatchReactor} always transmutes fuel into the same
composition, so the nuclide level flows are unrealistic for the full, 
multi-pass
recycle case.

@@

Figure \ref{fig:puseries1} shows the full-system plutonium buildup for open
(no recycle), modified open, and closed (infinite-pass recycle) variations of
the one-reactor scenario described above. The figure was
generated directly from \Cyclus output data. After several batch cycles (near
month 300) in the modified open and closed cases, enough separated fissile
material accumulates in the fuel fabrication facility to generate a full
recycled batch.  When this batch is transmuted, more plutonium is burned than
created.  This results in a drop in the total fuel cycle system plutonium
inventory.  This pattern repeats roughly every 10 cycles (200 months) for the
modified open case and every 9 cycles (180 months) for the closed case.
Because the modified open scenario does not re-recycle material, it takes the
fabrication facility 1 cycle longer to accumulate a full batch of
fissile material.

### 2015-01-14 fundamentals/impl.tex

The architecture of \Cyclus allows developers 
to define nuclear fuel cycle agents and processes independent of the simulation 
logic. This encapsulated `plug-in'
design choice provides two major benefits. First, analysts across research institutions can take advantage of the 
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to 
their specific problem. This 
mend-and-extend paradigm, common in modern software development, reduces 
maintenance overhead and improves code robustness by protecting the core logic 
from changes in the extensions. 
The researcher can focus on creating or customizing nuclear 
facility, institution, resource, and toolkit models within their specific area 
of technical expertise. This extensibility, magnified by an open source 
development process, frees the community of users to contribute desired 
features, independent from the team of \Cyclus core developers. 
% we could use a specific example of Cosi's equivalence method below
Second, because \Cyclus uses a modular archetype approach, comparing two 
archetypes is straightforward. For example, if an analyst would like 
to compare the effect of using different models to determine the input fuel 
composition for fast reactors, a variety of fuel fabrication archetypes can be 
developed and interchanged while keeping the rest of the fuel cycle fixed
 to compare fuel fabrication designs.

@@

Interchangeability is accomplished by providing \glspl{API} that define agent-to-agent
interaction and agent-to-environment interaction, primarily through the
\Class{Agent} and \Class{Trader} interfaces. Figure \ref{fig:agent_uml} shows 
the ``inheritance'' structure of the \Class{Agent} class in a \gls{UML} diagram 
format. It shows how the \Class{Agent} interface
provides a notion of parent-child hierarchichal relationship, where parents can
choose to \textit{deploy} child agents and \textit{decommission} child
agents. For the archetype developer, this interface provides enormous power
very simply. The \gls{API} provides the \Class{Agent} with helpful functionality for 
interacting with the \Cyclus simulation kernel while abstracting away unnecessary 
detail.

@@

Two primary consequences arise from this structure. First, institutions are
nominally
responsible for deploying and decommissioning facilities. Accordingly, advanced
logic regarding building and decommissioning can be obtained by subclassing the
\Class{Institution} interface. Second, the \Class{Facility} class implements the
\Class{Trader} interface, and thus institutions and regions, respectively, can
adjust the resource flow preferences of their managed facilities. Importantly,
this capability allows for the modeling of preferential regional trading
of resources (e.g., tariffs) as well as preferential institutional trading
(e.g., long-term contracts).

>>>>

The architecture of \Cyclus allows developers 
to define nuclear fuel cycle agents and processes independent of the simulation 
logic. This encapsulated `plug-in'
design choice provides two major benefits. First, analysts across research institutions can take advantage of the 
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to 
their specific problem. This 
mend-and-extend paradigm, common in modern software development, reduces 
maintenance overhead and improves code robustness by protecting the core logic 
from changes in the extensions. 
The researcher can focus on creating or customizing nuclear 
facility, institution, resource, and toolkit models within their specific area 
of technical expertise. This extensibility, magnified by an open source 
development process, frees the community of users to contribute desired 
features, independent from the team of \Cyclus core developers. 
Second, because \Cyclus uses a modular archetype approach, comparing two 
archetypes is straightforward. For example, if an analyst would like 
to compare the effect of using different models to determine the input fuel 
composition for fast reactors, a variety of fuel fabrication archetypes can be 
developed and interchanged while keeping the rest of the fuel cycle fixed
 to compare fuel fabrication designs.

@@

Interchangeability is accomplished by providing \glspl{API} that define agent-to-agent
interaction and agent-to-environment interaction, primarily through the
\Class{Agent} and \Class{Trader} interfaces. Figure \ref{fig:agent_uml} shows 
the ``inheritance'' structure of the \Class{Agent} class in a \gls{UML} diagram 
format. It shows how the \Class{Agent} interface
provides a notion of parent-child hierarchical relationship, where parents can
choose to \textit{deploy} child agents and \textit{decommission} child
agents. For the archetype developer, this interface provides enormous power
very simply. The \gls{API} provides the \Class{Agent} with helpful functionality for 
interacting with the \Cyclus simulation kernel while abstracting away unnecessary 
detail.

@@

Two primary consequences arise from this structure. First, institutions are
nominally
responsible for deploying and decommissioning facilities. Accordingly, advanced
logic regarding building and decommissioning can be obtained by inheriting 
those behaviors from the
\Class{Institution} interface. Second, the \Class{Facility} class implements the
\Class{Trader} interface, and thus institutions and regions, respectively, can
adjust the resource flow preferences of their managed facilities. Importantly,
this capability allows for the modeling of preferential regional trading
of resources (e.g., tariffs) as well as preferential institutional trading
(e.g., long-term contracts).
